%-------------------------
% Resume in Latex
% Original Author : Sourabh Bajaj
% Collaborators : Fabián Souza Di Paula
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemItalic}[3]{
  \item\small{
    \textbf{#1 (\textit{#2})}{: #3 \vspace{-2pt}}
  }\vspace{-4pt}
}

\newcommand{\resumeItemAlign}[2]{
  \vspace{-1pt}\item\small{
    \textbf{#1} \hfill \textit{#2}
  }\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
% CV STARTS HERE


\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{{\Large Fabián Souza Di Paula}}
\end{center}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  DNI. 93770425 & Email : \href{mailto:fsouzadi1995@gmail.com}{fsouzadi1995@gmail.com}\\
  Díaz Colodrero 2755, Buenos Aires & Mobile : (+54) 9 11 33156498\\
  1995/12/12 & LinkedIn: \href{https://www.linkedin.com/in/fsouzadi1995/}{/in/fsouzadi1995/}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {ORT Argentina}{Buenos Aires}
    {Computer Science}{Aug 2019 - Present}
  \resumeSubheading
    {Instituto CENS 63}{Buenos Aires}
    {Computing and technology}{2016}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
	\resumeSubheading
		{Hexacta}{Buenos Aires}
		{Ssr. FullStack Developer @ Farmacity}{Nov 2020 - Present}
			\resumeItemListStart
				\resumeItem{Backend}
					{Extension of the digital invoice data flow to persist payment information and arranging it into the actual invoice for visualization.}  \newline
				\resumeItem{Frontend}
					{Replatforming of specific application modules from Vue.js to Angular 8. Refactor of a monolith Angular application architecture by modularizing features to favor reusability.}  	\newline
	\resumeItemListEnd



	\resumeSubheading
		{Accenture SRL}{Buenos Aires}
		{Associate Software Engineer @ CIO LAD Latam}{Jul 2018 - Nov 2020}
			\resumeItemListStart
 				\resumeItem{Backend}
					{REST APIs: notifications API, serving parameterized resources (images, jsons, texts, reports, pdf generation) under .NET Framework / .NET Core.} \newline

				\resumeItem{Frontend}
					{Full-stack development of applications using .NET MVC, SQL Server and Javascript.} \newline
					{Development of Angular applications from scratch together with Azure Integration, admin features and the latest UI/UX modules implementing Angular Material and Angular Ant Design.}
			\resumeItemListEnd
\resumeSubHeadingListEnd

%----------LANGUAGES-----------------
\section{Languages}
\resumeSubHeadingListStart	
	\resumeItem{C Sharp} 
	{ASP.NET, ADO.NET, LINQ, .NET MVC, RESTful Web Services, SOA.}
	\resumeItem{Javascript, Typescript, HTML5, CSS3}{Semantic HTML. SASS/SCSS preprocessors. ES5+ language specifications.}\\
	\resumeItem{MS SQL Server} 
	{Transact-SQL, scripts, functions, stored procedures, triggers.}\\
	
\resumeSubHeadingListEnd


%----------FRAMEWORKS-----------------
\section{Frameworks}
\resumeSubHeadingListStart
  \resumeItem{.NET Core}
    {.NET Core from version 3.0 onwards.}\\
  \resumeItem{Entity Framework}
    {Entity frameworks ranging from version 5 to 6.}\\
  \resumeItem{Angular}
    {Angular ranging from version 4 to 11. Modular architecture. Angular CLI. RxJS. Internal/3rd party client API consumption. OAuth2 Authorization flow. Firebase integration (Auth, Firestore, Storage). DI. Interceptors. Custom Pure Pipes. Reactive Forms.}
\resumeItem{Unit testing}
	{Jasmine, Jest and Karma as test runner.}
\resumeItem{UI libraries}
	{Angular Material.  TailwindCSS. Ant-D-Zorro.}
\resumeSubHeadingListEnd



%----------SKILLS, METHODOLOGIES AND TOOLING-----------------
\section{Skills,  methodologies and tooling}

\resumeSubHeadingListStart
	\resumeItemAlign{Responsive Design}{}
	\resumeItemAlign{Yarn / npm / Webpack}{}
	\resumeItemAlign{NuGet Package Manager}{}
	\resumeItemAlign{Git / TFS / VSTS / Azure DevOps}{}
	\resumeItemAlign{Agile Methodologies (Scrum and Pair Programming) }{}
\resumeSubHeadingListEnd

\end{document}
